---
title: "Cabbages"
author: "Filipe"
date: "September 22, 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  

 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

c39 had an average of 51.5.   
c52 cultivation had a average of 64.4. 

there is a difference in average VitC between c39 and c52 cultivation methods. 

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Question: is there a difference in average VitC between c39 and c52? 

$H_0$: there is no difference in the average vitamin C content between c39 and c52 cultivation       methods. 


$H_A$: there is a difference in the average vitamin C content between c39 and c52 cultivation methods.        
Numerical~Cat

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
boxplot(VitC~Cult,data=veggy,main="Visualizing Vitmanin C Content")
```

this boxplot shows that c52 is more effective in producing higher vitamin C levels compared to c39.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```

the numerical results show us the difference in means which is 12.9. c52 has 12.9 more vitamin C than c39. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult,data=veggy)
```

the p-value = 3.405e-08 which means I reject the null hypothesis. The Welch Two Sample t-test shows that the c39 and c52 cultivation method is statistically significant and the cultivation method has a significant impact on vitamin C content. this would mean that $H_A$ is true. there is a difference in the average vitamin C content between c39 and c52 cultivation methods.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

in conclusion, the graphical, numerical, and inferential results prove that there is a significant difference in vitamin C content between the c39 and c52 cultivation methods. the low p-value gives us evidence against the null hypothesis, which means that the differences we found is unlikely to happen by chance. 
